Turned on!": Momentum in Round-Based First Person Shooter Esports

### 2022-07-20 presentation.qmd
remove notes

::: fragment
-   Search and Destroy (SnD) in Call of Duty (COD)
-   2020-2022 Call of Duty League (CDL) matches (qualifiers and majors)
-   4v4.
-   First to 6 round wins
-   Teams swap sides (offense and defense) after every round
:::

::: fragment
-   Plant/Defuse in Valorant
-   Valorant Champions Tour (VCT) matches (qualifiers and majors), through November 11, 2021
-   5v5
-   First to 13 round wins
-   One team plays offense in 12 consecutive rounds before swapping sides
-   Must win by 2 cod_rounds
:::

@@

::: notes
-   This should hint at what I'm calling the "4-4" phenomenon, where the o round win % is dramatically higher than adjacent scenarios (3-4, 4-3, 5-4, 4-5, and even 3-3 or 5-5).
-   Note that round win %s are lower than one might expect in 0-5 and 1-5 states.
:::

@@

::: notes
-   This should emphasize the ends of the spectrum seen on the previous graph.
:::

@@

::: notes
-   Big difference compared to COD. Lower/higher percentages in the corners are probably more indicative of gaps in team skill.
-   1-0, 1-1, 3-0, 3-1 seem to b e the biggest outliers.
:::

@@

::: notes
-   This is mostly just for reference. I think the next slide should have more insight, since it's harder to have a prior understanding about the probability of winning the series given a round state.
:::

@@

::: notes
-   Note the 4-4 and 2-4 series win percentages.
:::

@@

::: notes
-   This might be considered an "information-neutral" setting
:::

@@

::: notes
-   There should be evidence of 6-0's and 6-1's are more frequent than expected given 50-50% chances.
-   Notably 6-4's occur less frequently than expected
-   p-values are not significant for any
:::

@@

-   Round win % after a streak of 3 round wins:
-   Expected: **`r 100 * round(prob_n6_k3, 3)`%**
-   Actual: **`r 100 * round(cod_round_win_prop_after_b2b2b_wins$prop, 3)`%** (`r cod_round_win_prop_after_b2b2b_wins$n` / `r cod_round_win_prop_after_b2b2b_wins$total`)

::: notes
-   Note this is sort of biased by the fact that teams end up winning series in 6 cod_rounds more often than expected.
:::

>>>>

::: fragment
### Search and Destroy (SnD) in Call of Duty (COD)

-   2020-2022 Call of Duty League (CDL) matches (qualifiers and majors)
-   4v4.
-   First to 6 round wins
-   Teams swap sides (offense and defense) after every round
:::

<br/>

::: fragment
### A Plant/Defuse in Valorant

-   2021 Valorant Champions Tour (VCT) matches (qualifiers and majors)
-   5v5
-   First to 13 round wins
-   One team plays offense in 12 consecutive rounds before swapping sides
-   Must win by 2 cod_rounds
:::

@@

@@

@@

@@

@@

@@

@@

@@

Round win % after a streak of 3 round wins:

-   Expected: **`r 100 * round(prob_n6_k3, 3)`%**
-   Actual: **`r 100 * round(cod_round_win_prop_after_b2b2b_wins$prop, 3)`%** (`r cod_round_win_prop_after_b2b2b_wins$n` / `r cod_round_win_prop_after_b2b2b_wins$total`)
